---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pagecryptr

<!-- badges: start -->
<!-- badges: end -->

The goal of pagecryptr is to provide and R-wrapper around the [PageCrypt HTML password protecter](https://www.maxlaumeister.com/pagecrypt/). It is very common for R users to knit Rmarkdown documents to HTML docs. This provides an easy way to PageCrypt those documents without leaving R. The package has one function self named `pagecryptr` that uses the V8 package to run the JavaScript code that encrypts the document which usually occurs in the browser if using the PageCrypt website. Note this R package now currently runs the legacy version of PageCrypt.

## Installation

You can install the development version of pagecryptr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("brentscott93/PageCrypt/pagecryptr")
```


## Example

```{r example}
library(pagecryptr)
if(interactive()){
 file <- system.file("example.html", package = "pagecryptr")
 pagecryptr(file, "password", out_file = "~/Desktop/encrypted-file.html")
}
```

